Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-12 article.tex
Put most exporatory study in supmat

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.
One could assume a two-state fitness landscape: being
undetected, due to zero epitopes, or being detected, due to one or more
epitopes. Alternatively, one may hypothesize a gradual fitness decrease per
extra epitope. Both fitness landscapes are depicted in 
figure \ref{fig:fitness_landscape}.

Would the pathogen have many epitopes, this study needs to 
assume a gradual fitness landscape. Due to this, we did a simple 
exploratory experiment (see 'Fitness landscape', 
subsection \ref{subsec:fitness_landscape}) in which
we counted the number of epitopes in COVID-19. Because the number
of epitopes has decreased, we dared to assume a gradual fitness landscape
and to proceed with the full experiment.

@@

\paragraph{Reason to do before actual experiment}
This exploratory experiment tests an assumptions 
of the bigger evolutionary experiment. 
If the assumption is incorrect,
a different evolutionary experiment needs to be contrived.

\paragraph{Method in general}
For a given MHC-I haplotype, we count the number of epitopes in 
the proteome of COVID-19, at the start of the 2019 pandemic (as
described in \cite{wu2020new})
and a random strain sequenced most recently at the day of the experiment. 
Of both proteomes, we use use \verb;epitope-prediction; \cite{bianchi2017} 
to count the number of predicted binders for the HLA-A-02:01 haplotype.

>>>>

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.

This study assumes a gradual fitness landscape, in which it always
(slightly) beneficial for a pathogen to lose an epitope.
Because this assumption needs to be correct for the research
to be viable, we did an
exploratory experiment (see 'Fitness landscape', 
subsection \ref{subsec:fitness_landscape}).
We concluded that the assumption may be correct.

@@

\paragraph{Introduction}
One could assume a two-state fitness landscape: being
undetected, due to zero epitopes, or being detected, due to one or more
epitopes. Alternatively, one may hypothesize a gradual fitness decrease per
extra epitope. Both fitness landscapes are depicted in 
figure \ref{fig:fitness_landscape}.

\paragraph{Why}
This exploratory experiment tests an assumptions 
of the bigger evolutionary experiment. 
If the assumption is incorrect,
a different evolutionary experiment needs to be contrived.

\paragraph{Method}
For a given MHC-I haplotype, we count the number of epitopes in 
the proteome of COVID-19, at the start of the 2019 pandemic (as
described in \cite{wu2020new})
and a random strain sequenced most recently at the day of the experiment. 
Of both proteomes, we use use \verb;epitope-prediction; \cite{bianchi2017} 
to count the number of predicted binders for the HLA-A-02:01 haplotype.
We use that haplotype, as it is the haplotype used by default with the
\verb;epitope-prediction; package.
